Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-04-15 ms.tex
added the model fits.

\title{Back to Normal Transits for the Disintegrating Planet Candidate KIC 12557548 b}

@@

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.8\textwidth]{images/kepler/secondary_eclipse.pdf}
\caption{Secondary eclipse found by averaging the light curve from 17 quarters of Kepler data.}\label{fig:secEclipse}
\end{centering}
\end{figure*}

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/photometry_riverplot.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/pca_k1255.pdf}
\caption{Cleaned Kepler Long-cadence data and PCA analysis.}\label{fig:kepPCA}
\end{centering}
\end{figure*}

@@

>>>>

\title{Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b}

@@

@@

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/kepler/secondary_eclipse.pdf}
\caption{Secondary eclipse found by averaging the light curve from 17 quarters of Kepler data.}\label{fig:secEclipse}
\end{centering}
\end{figure*}

We create a cleaned Kepler long-cadence data set by interpolating all time series data onto a fixed phase grid with a spacing of 30 minutes.

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/photometry_riverplot.pdf}
\includegraphics[width=0.49\textwidth]{images/kepler/model_riverplot.pdf}
\caption{Cleaned Kepler Long-cadence data (Left) and model fit (Right).}\label{fig:kepPCA}
\end{centering}
\end{figure*}

We take the dot product ($\bullet$) with the first principal component to create an amplitude time series.
\begin{equation}
A = \frac{(f - 1) \bullet c_1}{c_1 \bullet c_1},
\end{equation}
where $A$ is the amplitude vector, $f$ is the flux matrix with x indices of time and y indices of transit number and $c_1$ is the vector of the first principal component .

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/pca_k1255.pdf}
\includegraphics[width=0.45\textwidth]{images/kepler/amplitude_series.pdf}
\caption{Principal component eigenvectors (Left) and amplitude time series (Right).}\label{fig:secEclipse}
\end{centering}
\end{figure*}
